Potential and limits of site-specific substitution model inference.

### 2019-12-30 manuscript/ms.tex
edited affiliations

\title{Potential and limits of site-specific substitution model inference.}
\author{Vadim Puller$^{1,2,3}$ Pavel Sagulenko$^{1}$, Richard Neher$^{1,2,3}$}
\affiliation{$^{1}$Max Planck Institute for Developmental Biology, 72076 T\"ubingen, Germany\\
$^{2}$Biozentrum, University of Basel, Klingelbergstrasse 50/70, 4056 Basel, Switzerland\\
$^{3}$SIB Swiss Institute of Bioinformatics, Basel, Switzerland}

>>>>

\title{Potential and limits of site-specific substitution model inference.}
\author{Vadim Puller$^{1,2}$ Pavel Sagulenko$^{3}$, Richard Neher$^{1,2}$}
\affiliation{
$^{1}$Biozentrum, University of Basel, Klingelbergstrasse 50/70, 4056 Basel, Switzerland\\
$^{2}$SIB Swiss Institute of Bioinformatics, Basel, Switzerland\\
$^{3}$Max Planck Institute for Developmental Biology, 72076 T\"ubingen, Germany}
